% =============================================================================
\section{Humanitarian Crisis Response}
% =============================================================================

The Persian diaspora has repeatedly mobilized during crises---earthquakes, floods, political upheaval, and now ongoing humanitarian emergencies. MIGA provides permanent infrastructure for these efforts.

\subsection{Current Crisis: Why This Matters Now}

Iran faces compounding humanitarian challenges:
\begin{itemize}
    \item \textbf{Economic collapse}: Currency devaluation, unemployment, poverty
    \item \textbf{Healthcare crisis}: Sanctions impacting medicine and equipment
    \item \textbf{Brain drain}: Millions fleeing, families separated
    \item \textbf{Political repression}: Ongoing human rights violations
    \item \textbf{Environmental}: Water crisis, pollution, climate impacts
\end{itemize}

\begin{tcolorbox}[colback=red!10,title={\textbf{Urgent Need}}]
The diaspora sends an estimated \$10--20 billion annually to Iran through informal channels. MIGA can make this transparent, efficient, and impactful---while protecting senders and recipients.
\end{tcolorbox}

\subsection{DAO Response Framework}

Each of the 10 DAOs has specific humanitarian functions:

\begin{center}
\begin{tabular}{p{2cm}p{4cm}p{6cm}}
\toprule
\textbf{DAO} & \textbf{Crisis Function} & \textbf{Example Actions} \\
\midrule
SAL (Health) & Medical aid & Medicine procurement, doctor networks, mental health support \\
AMN (Security) & Protection & Secure communications, identity protection, evacuation support \\
KHAZ (Treasury) & Emergency funds & Rapid disbursement, currency stabilization aid \\
PAY (Consular) & Coordination & Family reunification, legal aid, visa support \\
FARH (Culture) & Preservation & Document archives, artist support, language programs \\
DAN (Research) & Documentation & Human rights reports, crisis monitoring, data collection \\
WAQF (Endowment) & Long-term & Orphan funds, education scholarships, rebuilding reserves \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Emergency Response Mechanisms}

\textbf{1. Rapid Response Fund}
\begin{itemize}
    \item 5\% of treasury in stablecoin emergency reserve
    \item Can be deployed within 24 hours with multi-sig approval
    \item Pre-approved partner organizations for distribution
\end{itemize}

\textbf{2. Crisis Governance Mode}
\begin{itemize}
    \item Shortened voting periods (24 hours vs. 5 days)
    \item Lower quorum requirements for emergency proposals
    \item Automatic sunset after crisis ends
\end{itemize}

\textbf{3. Mutual Aid Networks}
\begin{itemize}
    \item Chapter-to-chapter coordination for refugee support
    \item Professional networks (doctors, lawyers, engineers)
    \item Housing and employment assistance databases
\end{itemize}

\subsection{Privacy-Preserving Aid}

For people in dangerous situations:
\begin{itemize}
    \item \textbf{Shielded disbursements}: Recipients cannot be traced
    \item \textbf{Plausible deniability}: Multiple-hop transfers
    \item \textbf{Verified impact}: Zero-knowledge proof of delivery
    \item \textbf{Protected voting}: Beneficiaries can participate safely
\end{itemize}

\subsection{Accountability Without Exposure}

\begin{tcolorbox}[colback=migagold!10]
\textbf{Public}: Total funds disbursed, impact metrics, audit reports\\
\textbf{Private}: Individual recipients, transfer routes, operator identities
\end{tcolorbox}

The MIZ (Integrity) DAO conducts quarterly impact audits. Results are published. Names are not.
